### 2021-10-14 paper/paper.tex

\vskip 6pt
\cit is one of a few common strategies for automated test case generation. A randomized strategy chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}. Some tools introduce more structure to choosing random arguments. The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases~\cite{loscher2018automating}. Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh,vira2019}. We will compare these methods in Sec.~\ref{sec:comparison}, after we understand the scope of combinatorial interaction testing.

>>>>

\vskip 6pt
\cit is one of a few common strategies for automated test case generation. A randomized strategy chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}. Some tools introduce more structure to choosing random arguments. The \href{https://hackage.haskell.org/package/QuickCheck}{\texttt{QuickCheck}}(Haskell) and \href{https://github.com/HypothesisWorks/hypothesis}{\texttt{Hypothesis}} (Python) packages use customized generators to create streams of test cases~\cite{loscher2018automating}. Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh,vira2019}. We will compare these methods in Sec.~\ref{sec:comparison}, after we understand the scope of combinatorial interaction testing.
